Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
nouns to verbs

This work introduces Moltres, a new physics application for multiphysics
modeling of fluid-fuelled molten salt reactors. The neutronics model, thermal
hydraulics model, and their coupling in the MOOSE framework are
described. Neutron and precursor equations are implemented using an Action
system that allows use of an arbitrary number of groups with no change in the
input card. Results for many-channel configurations in 2D-axisymmetric and 3D
coordinates are presented. These are compared against other coupled models as
well as the Molten Salt Reactor Experiment.

>>>>

This work introduces Moltres, a new physics application for modeling coupled 
physics in fluid-fuelled, molten salt reactors. The neutronics model, thermal
hydraulics model, and their coupling in the MOOSE framework are
described. Neutron and precursor equations are implemented using an Action
system that allows use of an arbitrary number of groups with no change in the
input card. Results for many-channel configurations in 2D-axisymmetric and 3D
coordinates are presented and compared against other coupled models as
well as the Molten Salt Reactor Experiment.
